### 2022-07-26 README.Rmd
Added seeds on examples

object = bremla(formula,data,reference.label="GICC05",
                nsims=5000,
                events=events,
                synchronization=list(method="adolphi"),
                control.fit=list(method="inla"),
                control.sim=list(synchronized=TRUE),
                print.progress=TRUE )
summary(object)
```

```{r plot, message=FALSE, eval=TRUE, echo=FALSE}
require(ggplot2)
free_indexes = x$tie_points$free_indexes
tie_indexes = x$tie_points$tie_indexes
ageref_free = x$data$age[free_indexes]
ageref_tie = x$data$age[tie_indexes]

fullpd = data.frame(depth = x$data$depth[free_indexes],
                medians=x$simulation$summary_sync$median[free_indexes]-ageref_free,
                lower=x$simulation$summary_sync$lower[free_indexes]-ageref_free,
                upper=x$simulation$summary_sync$upper[free_indexes]-ageref_free)

@@

gg2 = gg2 + geom_segment(data=data.frame(depth=x$data$depth[tie_indexes],                                          median=x$simulation$summary_sync$median[tie_indexes]-ageref_tie,                               lower=x$simulation$summary_sync$lower[tie_indexes]-ageref_tie,
                    upper=x$simulation$summary_sync$upper[tie_indexes]-ageref_tie),
                    aes(x=.data$depth,y=.data$lower,xend=.data$depth,yend=.data$upper),
                    col="magenta")
print(gg2)
```

>>>>

results = bremla(formula,data,reference.label="GICC05",
                nsims=5000,
                events=events,
                synchronization=list(method="adolphi"),
                control.fit=list(method="inla"),
                control.sim=list(synchronized=TRUE) )
summary(results)
```

```{r plot, message=FALSE, eval=TRUE, echo=FALSE}
require(ggplot2)
free_indexes = results$tie_points$free_indexes
tie_indexes = results$tie_points$tie_indexes
ageref_free = results$data$age[free_indexes]
ageref_tie = results$data$age[tie_indexes]

fullpd = data.frame(depth = results$data$depth[free_indexes],
                medians=results$simulation$summary_sync$median[free_indexes]-ageref_free,
                lower=results$simulation$summary_sync$lower[free_indexes]-ageref_free,
                upper=results$simulation$summary_sync$upper[free_indexes]-ageref_free)

@@

gg2 = gg2 + geom_segment(data=data.frame(depth=results$data$depth[tie_indexes],                                   median=results$simulation$summary_sync$median[tie_indexes]-ageref_tie,                         lower=x$simulation$summary_sync$lower[tie_indexes]-ageref_tie,
                   upper=results$simulation$summary_sync$upper[tie_indexes]-ageref_tie),
                   aes(x=.data$depth,y=.data$lower,xend=.data$depth,yend=.data$upper),
                   col="magenta")
print(gg2)
```
